### 2016-02-25 config/styles.inc.tex
Clean up chapter 3
More work on derivatives of O(2) sys
Some small changes to graphics in CH02

\pgfplotsset{compat=newest}

@@

@@

@@

\pgfplotsset{percentileLines/.style={black,dashed}}
\tikzset{annotation/.style={align=left,draw=black!0.2,font=\scriptsize,fill=white,fill opacity=0.8}}

>>>>

\pgfplotsset{compat=newest}
%http://tex.stackexchange.com/questions/18152/how-can-i-adjust-the-horizontal-spacing-between-legend-entries-in-pgfplots

@@

\pgfplotsset{legendAbovePlot/.style={legend style={at={(0.5,1.025)},anchor={south},nodes=right,legend columns=-1,font=\footnotesize,draw=none,/tikz/every even column/.append style={column sep=1em}}}}

@@

\pgfplotsset{myDerivs/.style={color=black,solid,line width=1.0pt}}

@@

\pgfplotsset{percentileLines/.style={black,dashed}}
%NOTE: we need tikzset here, these styles are used on NODE (\in TikZ) instead of Pgfplots stuff
\tikzset{annotation/.style={align=left,draw=black!0.2,font=\scriptsize,fill=white,fill opacity=0.8}}

\tikzset{numSlope/.style={anchor=center,align=center,font=\scriptsize}}
